---
title: "Masters Example for Running GLMER and LMER Models with lme4"
author: "TJ Wukitsch"
date: "July 2023"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Workspace Setup

## Install and Load Required Packages

If you haven't already downloaded and installed Rtools, please install Rtools from https://cran.r-project.org/bin/windows/Rtools/ and restart R. The C++ compiler is required for some of the packages that you are about to install. 

The following code will check and remind you if you haven't yet installed Rtools. Then it will check to see if the package is already downloaded and installed. If so, it will simply load the package. If not, it will install the package from CRAN and then load the package once the installation is complete. You may be prompted to allow some of the downloads to take place so please remain at your device.

```{r load packages}
# Load Packages ####

# See if rtools is installed. It has necessary C++ compiler for installs of some of the libraries that are required.
if (Sys.which("make") == "") {  # Check to see if "make" command from rtools is found in system's PATH. If an empty string is retuned, rtools isn't installed.
  message("Rtools is not found. Please install Rtools from https://cran.r-project.org/bin/windows/Rtools/ and restart R.")
} else { #rtools installed == TRUE
  message("Rtools is installed.")
  
  # Load package or install MASS and load if not present
  if (!require(MASS)) {
    install.packages("MASS")
    library(MASS)
  }
  
  # Load package or install lattice and load if not present
  if (!require(lattice)) {
    install.packages("lattice")
    library(lattice)
  }
  
  # Load package or install boot and load if not present
  if (!require(boot)) {
    install.packages("boot")
    library(boot)
  }
  
  # Load package or install car and load if not present
  if (!require(car)) {
    install.packages("car")
    library(car)
  }
  
  # Load package or install emmeans and load if not present
  if (!require(emmeans)) {
    install.packages("emmeans")
    library(emmeans)
  }
  
  
  # Load package or install lme4 and load if not present
  if (!require(lme4)) {
    install.packages("lme4")
    library(lme4)
  }
  
  # Load package or install zoo and load if not present
  if (!require(zoo)) {
    install.packages("zoo")
    library(zoo)
  }
  
  # Load package or install tidyr and load if not present
  if (!require(tidyr)) {
    install.packages("tidyr")
    library(tidyr)
  }
  
  # Load package or install ggplot2 and load if not present
  if (!require(ggplot2)) {
    install.packages("ggplot2")
    library(ggplot2)
  }
  
  # Load package or install lmerTest and load if not present
  if (!require(lmerTest)) {
    install.packages("lmerTest")
    library(lmerTest)
  }
  
  # Load package or install dplyr and load if not present
  if (!require(dplyr)) {
    install.packages("dplyr")
    library(dplyr)
  }
  
  # Packages that may be needed, maybe not:
  
  # Load package or install multcomp and load if not present
  if (!require(multcomp)) {
    install.packages("multcomp")
    library(multcomp)
  }
  
  # Load package or install foreign and load if not present
  if (!require(foreign)) {
    install.packages("foreign")
    library(foreign)
  }
  
  # Load package or install msm and load if not present
  if (!require(msm)) {
    install.packages("msm")
    library(msm)
  }
  
  # Load package or install effects and load if not present
  if (!require(effects)) {
    install.packages("effects")
    library(effects)
  }
  
  
  print("******** INSTALLATION AND LOADING COMPLETE ********")
} #end rtools installed == TRUE
```

##Set your working directory

```{r Working Directory}
#Set your working directory to your project folder and check that it is correct
setwd("C:/Users/kieri/Documents/ABHV/")
getwd()
```

# Workspace Overview

To keep an organized and uncluttered workspace, I use a set of hierarchical lists to store related objects for project analyses.
We have the following object categories with most analyses:
* data
* models
* comparisons
* plots

In this specific set of analyses we have a number of needs that determine the objects in each category.

## Data

The full data requires various sub-setting to ensure the correct substances are being assessed independently and that controls that never received access to ethanol are not included when it would be inappropriate to do so. Thus, my data list object will look like this with abbreviated names for easier calling:

* data
  * raw
  * ethanol
    * with controls
    * no controls
  * sucrose
    * with controls
    * no controls
  * water
    * with controls
    * no controls

To do this we generate a list called `data` and begin populating it with subsets of the original data. In addition we adjust the contrast coding and scale of some of our variables to help us avoid problems later. I adjust my categorical (factor) variables' contrast coding attributes because I want my GLMER models' categorical variables to be coded like an ANOVA to ease interpretation of the effects. In other words, I want my model's intercept to be at the Grand Mean. Thus, I must recode my categorical variables using sum-to-zero aka contrast coding instead of dummy coding or other types. One group is assigned +1 and the other is assigned -1 and they sum to zero.

```{r Data Subsetting}


data <- list()

# Read in data file with auto-headings and blanks/ N/As set to blank ("") and my categorical or character data read in as the data type "factor"
data$raw <- read.csv("C:/Users/Kieri/Documents/ABHV/ABHV2018.csv", na.strings="\"\"", stringsAsFactors = TRUE)
data$raw$RatID <- as.factor(data$raw$RatID) # Convert RatID to factor type because it is not a numeric variable although it seems like one.
      # Change variable coding to contrast sum (sum-to-zero) coding. 
      # This attribute will be inherited for all data frames subset from this one, so it is a good idea to perform this step now for parsimonious code.
        # adjust Age to contrast coding
        contrasts(data$raw$Age)=contr.sum(2)
        contrasts(data$raw$Age)
        # adjust Condition to contrast coding
        contrasts(data$raw$Condition)=contr.sum(2)
        contrasts(data$raw$Condition)
      
View(data$raw)

# Subsetting Substances ####

  # Ethanol
    # With Controls
    data$eth$ctrl <- subset(data$raw, Substance == "Ethanol")
      # Rescale -- to avoid issues with eigen values later
      data$eth$ctrl$recoded.conc <- car::recode(data$eth$ctrl$Concentration, "5 =.05; 20 =.20; 40 =.40")
      
    # No Controls
      # Subset rats that could drink ethanol from rats that never had the opportunity
    data$eth$no.ctrl <- subset(data$eth$ctrl, Condition != "CTRL")
    
    # View your data frames in RStudio
    View(data$eth$ctrl)
    View(data$eth$no.ctrl)
  
    
  # Sucrose
    # With Controls
    data$suc$ctrl <- subset(data$raw, Substance == "Sucrose")
      # Rescale -- to avoid issues with eigen values later
      data$suc$ctrl$molarity <- car::recode(data$suc$ctrl$Concentration, ".34=.01; 3.4=.1; 34=1")

    # No Controls
      # Subset rats that could drink ethanol from rats that never had the opportunity
    data$suc$no.ctrl <- subset(data$suc$ctrl, Condition != "CTRL")
    
    # View your data frames in RStudio
    View(data$suc$ctrl)
    View(data$suc$no.ctrl)
  
    
  # Water
    # With Controls
    data$h2o$ctrl <- subset(data$raw, Substance == "Water1" | Substance == "Water2")
      # Get rid of the 4 levels of Substance inherited from the original dataset
      data$h2o$ctrl$Substance <- factor(data$h2o$ctrl$Substance)
      #Adjust contrasts to sum-to-zero
      contrasts(data$h2o$ctrl$Substance)=contr.sum(2)
      contrasts(data$h2o$ctrl$Substance)
    # No Controls
      # Subset rats that could drink ethanol from rats that never had the opportunity
    data$h2o$no.ctrl <- subset(data$h2o$ctrl, Condition != "CTRL")      
    
    # View your data frames in RStudio
    View(data$h2o$ctrl)
    View(data$h2o$no.ctrl)
```

Now we have our data list object with the following hierarchical structure:

* `data`
  * `$raw`
  * `$eth`
    * `$ctrl`
    * `$no.ctrl`
  * `$suc`
    * `$ctrl`
    * `$no.ctrl`
  * `$h2o`
    * `$ctrl`
    * `$no.ctrl`

And I have performed my coding adjustments. However, I still need to further prepare our data to avoid issues during analysis such as problems with variance inflation. If I mean-center the continuous variables that will be predictors in an LMER or GLMER model, the variance inflation factor tends to remain within a tolerable range and doesn't affect results. Thus I mean-center the variables I need to below and save my workspace.

```{r Centering Variables}
# Centering Variables

  # Ethanol
    # center concentration to avoid issues with variance inflation factor (VIF) tolerances
    data$eth$ctrl$c.conc <- data$eth$ctrl$recoded.conc-mean(data$eth$ctrl$recoded.conc)
    # center TOTAL.ETOH.Swap.Consumed..g.kg. to avoid issues with variance inflation factor (VIF) tolerances
    data$eth$no.ctrl$c.totale <- data$eth$no.ctrl$TOTAL.ETOH.Swap.Consumed..g.kg.-mean(data$eth$no.ctrl$TOTAL.ETOH.Swap.Consumed..g.kg.)
    # center concentration fto avoid issues with variance inflation factor (VIF) tolerances
    data$eth$no.ctrl$c.conc <- data$eth$no.ctrl$recoded.conc-mean(data$eth$no.ctrl$recoded.conc)
    
    # center MAC and ROC to avoid issues with variance inflation factor (VIF) tolerances
    data$eth$no.ctrl$c.MAC <- data$eth$no.ctrl$MAC-mean(data$eth$no.ctrl$MAC)
    data$eth$no.ctrl$c.ROC <- data$eth$no.ctrl$ROC-mean(data$eth$no.ctrl$ROC)
    data$eth$no.ctrl$c.MAC3 <- data$eth$no.ctrl$MAC3-mean(data$eth$no.ctrl$MAC3)
    data$eth$no.ctrl$c.ROC3 <- data$eth$no.ctrl$ROC3-mean(data$eth$no.ctrl$ROC3)
  
    
  # Sucrose
    # Center molarity to avoid issues with variance inflation factor (VIF) tolerances
    data$suc$ctrl$c.molarity <- data$suc$ctrl$molarity-mean(data$suc$ctrl$molarity)
    data$suc$no.ctrl$c.molarity <- data$suc$no.ctrl$molarity-mean(data$suc$no.ctrl$molarity)
    #center TOTAL.ETOH.Swap.Consumed..g.kg. to avoid issues with variance inflation factor (VIF) tolerances
    data$suc$no.ctrl$c.totale <- data$suc$no.ctrl$TOTAL.ETOH.Swap.Consumed..g.kg.-mean(data$suc$no.ctrl$TOTAL.ETOH.Swap.Consumed..g.kg.)
    #center MAC and ROC for noCTRL subset to avoid issues with variance inflation factor (VIF) tolerances
    data$suc$no.ctrl$c.MAC <- data$suc$no.ctrl$MAC-mean(data$suc$no.ctrl$MAC)
    data$suc$no.ctrl$c.ROC <- data$suc$no.ctrl$ROC-mean(data$suc$no.ctrl$ROC)
    

  # Water
    #center TOTAL.ETOH.Swap.Consumed..g.kg. to avoid issues with variance inflation factor (VIF) tolerances
    data$h2o$no.ctrl$c.totale <- data$h2o$no.ctrl$TOTAL.ETOH.Swap.Consumed..g.kg.-mean(data$h2o$no.ctrl$TOTAL.ETOH.Swap.Consumed..g.kg.)
    
    #center MAC and ROC for noCTRL subset to avoid issues with variance inflation factor (VIF) tolerances
    data$h2o$no.ctrl$c.MAC <- data$h2o$no.ctrl$MAC-mean(data$h2o$no.ctrl$MAC)
    data$h2o$no.ctrl$c.ROC <- data$h2o$no.ctrl$ROC-mean(data$h2o$no.ctrl$ROC)

# Save the workspace
save.image("ABHV_workspace.RData")

```

## Models (Analyses)

To accommodate and store each list object returned by our models I need another hierarchical list object with a similar structure to the data above. However, there is more nuance because I am performing analyses for hedonic and aversive responses and, for each of those, I have analyses that involve different variables that were calculated from modeling other related data (total ethanol, MR, and MR3). So I will need a different list structure, and I may want to generate the list structure in advance so I can populate it with a list. It should look something like this:

* models
  * ethanol
    * aversive
      * overall
      * total ethanol
      * Mean Alcohol Consumed & Rate of Change
      * Mean Alcohol Consumed & Rate of Change excluding day 3
    * hedonic
      * overall
      * total ethanol
      * Mean Alcohol Consumed & Rate of Change
      * Mean Alcohol Consumed & Rate of Change excluding day 3
  * sucrose
    * aversive
      * overall
      * total ethanol
      * Mean Alcohol Consumed & Rate of Change
    * hedonic
      * overall
      * total ethanol
      * Mean Alcohol Consumed & Rate of Change
  * water
    * aversive
      * overall
      * total ethanol
      * Mean Alcohol Consumed & Rate of Change
    * hedonic
      * overall
      * total ethanol
      * Mean Alcohol Consumed & Rate of Change

```{r Generating Model List(s)}
models <- list()
 #will need to use list here
models$eth <- list()
models$suc <- list()
```






In the end, our specific lists of objects with abbreviations looks like this:

* data
  * raw
  * ethanol
    * with controls
    * no controls
  * sucrose
    * with controls
    * no controls
  * water
    * with controls
    * no controls
* models
  * ethanol
    * aversive
      * overall
      * total ethanol
      * MR (Mean Alcohol Consumed & Rate of Change)
      * MR3 (Mean Alcohol Consumed & Rate of Change excluding day 3)
    * hedonic
      * overall
      * total ethanol
      * MR (Mean Alcohol Consumed & Rate of Change)
      * MR3 (Mean Alcohol Consumed & Rate of Change excluding day 3)
  * sucrose
    * aversive
      * overall
      * total ethanol
      * MR (Mean Alcohol Consumed & Rate of Change)
    * hedonic
      * overall
      * total ethanol
      * MR (Mean Alcohol Consumed & Rate of Change)
  * water
    * aversive
      * overall
      * total ethanol
      * MR (Mean Alcohol Consumed & Rate of Change)
    * hedonic
      * overall
      * total ethanol
      * MR (Mean Alcohol Consumed & Rate of Change)
* comparisons
* plots

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
